---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# glmPredict

glmPredict extends the functionality of the `augment.glm` function of the `broom` package to make class predictions for a dataset with a Generalised Linear Model. This package was created for an assignment in [STAT545B](https://stat545.stat.ubc.ca/).

## Installation

You can install the development version from [GitHub](https://github.com/janetxinli/glmPredict) with:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("janetxinli/glmPredict")
```

## Example

We're going to predict the malignancy of samples in a cleaned version of the [Breast Cancer Wisconsin Dataset](https://archive.ics.uci.edu/ml/datasets/Breast+Cancer+Wisconsin+(Diagnostic)) by creating a simple Generalised Linear Model. The dataset, `cancer_clean`, is available in the `glmPredict` package, where it has been slightly shrunk down from the original. The final diagnosis of the samples are encoded by the `malignant` column, where a value of 1 means the sample was diagnosed as malignant, and a sample of 0 means the sample was benign.

First, we need to make the `glm`, with `family=binomial` or `family=quasibinomial` to specify the response as a factor. The data will be subsetted as well, so we have a set of unseen data to pass into `glm_predict` later.

```{r}
library(glmPredict)

# Start by subsetting the data
set.seed(123)
subset_len <- floor(0.75 * nrow(cancer_clean))
subset_ind <- sample(seq_len(nrow(cancer_clean)), size=subset_len)
cancer_subset <- cancer_clean[subset_ind,]
cancer_new <- cancer_clean[-subset_ind,]

# Create a glm with cancer_subset
(cancer_model <- glm(malignant ~ texture_mean + radius_mean, data=cancer_subset, family="binomial"))
```

Then, we can use the `cancer_model` to make predictions, setting the threshold for predicting the positive class (malignant in this case) to 0.6 for example purposes:

```{r}
(cancer_predictions <- glm_predict(cancer_model, "malignant"))
```

The function returns the `augment` object which contains the predictions (`.prediction` column) and some statistics. The function also returns the accuracy, precision and recall of the predictions. This data is grouped in a named list, so the components can be accessed by name or index:

```{r}
cancer_predictions$augment
cancer_predictions$precision
cancer_predictions[4]
```

You can also pass a different dataset (one not used to create the `glm`) to make predictions with `glm_predict`. To do so, you just need to specify the dataset with the `newdata` argument.

```{r}
glm_predict(cancer_model, "malignant", threshold=0.6, newdata=cancer_new)
```

## Code of Conduct

Please note that the glmPredict project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
