---
title: "glmPredict"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{glmPredict}
  %\VignetteEngine{knitr::rmarkdown}ß
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# glmPredict

glmPredict extends the functionality of the `broom::augment.glm` function by making predictions of the target variable class. The `glm_predict` function makes these predictions. It requires a fitted `glm` model object with `family=binomial` or `family=quasibinomial` as input, as well as the name of the target variable. This is analogous to making predictions on Logistic Regression model.
<br><br>
The class is predicted by comparing the response (the predicted probability of the positive class) to a threshold, 0.5 by default. The `threshold` argument can be changed to specify a higher or lower threshold for predicting the positivei class. By default, the model will predict on the data present in the `glm` model, but a different dataset with the same feature variables can be passed to the function with the `newdata` argument to make predictions on a new dataset.
<br><br>
This package also comes with various functions for evaluating a set of predictions. Accuracy can be evaluated with the `accuracy_score` function, precision can be calculated with `precision_score`, and `recall_score` calculates the recall of the predictions.
<br><br>
The `glmPredict` package also comes equipped with a toy dataset, `cancer_clean`, to use and test the functionality of `glm_predict()`. 
<br><br>
You can install the development version from [GitHub](https://github.com/janetxinli/glmPredict) with:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("janetxinli/glmPredict")
```

### Basic Usage

```{r setup}
library(glmPredict)
```

You can learn more about modelling in R and Generalised Linear Models [here](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/glm). For this demo, we'll be working with the `cancer_clean` dataset. The `cancer_clean` dataset is a simplified version of the [Breast Cancer Wisconsin Dataset](https://archive.ics.uci.edu/ml/datasets/Breast+Cancer+Wisconsin+(Diagnostic)). 
<br><br>
You can learn more about the dataset by typing `?cancer_clean` into your Rstudio console. Essentially, the dataset is a tibble with 569 rows and 11 columns. Each row represents measurements from a single breast mass biopsy image, and each column is a different metric describing the nuclei present in the image. The `malignant` column describes the final diagnosis of each sample, where 1 = malignant and 0 = benign.
<br><br>
First, we'll start by subsetting `cancer_clean` by row. `cancer_subset` will contain 75% of the rows in the original dataset, and `cancer_new` will contain the other 25%.

```{r prep-data}
set.seed(123)
subset_len <- floor(0.75 * nrow(cancer_clean))
subset_ind <- sample(seq_len(nrow(cancer_clean)), size=subset_len)
cancer_subset <- cancer_clean[subset_ind,]
cancer_new <- cancer_clean[-subset_ind,]
```

Say we want to predict whether a sample will be classified as malignant or benign (y) by taking into account the mean texture and mean radius (x) of nuclei in each image. We can create a `glm` with the `cancer_subset` dataset and the formula `y ~ x`. 

```{r create-model}
(cancer_model <- glm(malignant ~ texture_mean + radius_mean, data=cancer_subset, family="binomial"))
```

Now if we want to see which samples in `cancer_subset` our model predicts are malignant, we can use the `glm_predict` function:

```{r predict-subset}
(preds <- glm_predict(cancer_model, "malignant"))
```

Under the hood, `glm_predict()` runs `augment.glm(type.predict="response")` on the model. This returns the predicted probability of each sample being in the positive class, and `glm_predict()` compares this probability to a certain threshold to classify each sample as either positive (malignant) or negative (benign). The predictions are appended to the `augment.glm` tibble, and returned from the function.

The output of `glm_predict()` is the `augment` object from `augment.glm`, with an extra column `.prediction` containing the predicted label for each example.

### Predicting on new data

We can make predictions on new data that isn't in the `glm` model object, as well. We didn't use `cancer_new` when creating our model, but what if we want to see what the model predicts for those observations? In this case, we can pass `cancer_new` by specifying the `newdata` argument in the `glm_predict` function:

```{r newdata}
(preds_new <- glm_predict(cancer_model, "malignant", newdata=cancer_new))
```

### Changing threshold

Most often, a probability threshold of 0.5 is used to predict the positive class, but you might want to adjust this threshold if you want to be more or less strict with your predictions. In our case, the positive class is serious, and we would rather have more false positives than false negatives. We could decrease the threshold so we predict a sample as malignant more often. This can be done by specifying the `threshold` argument:

```{r threshold}
glm_predict(cancer_model, "malignant", threshold=0.4)
```

### Evaluating predictions

The correctness of the predictions can be evaluated with several metrics, such as accuracy, prediction and recall. `glmPredict` provides functions to calculate these three metrics: `accuracy_score`, `precision_score` and `recall_score`. To use these functions, we need to compare the "ground truth" labels to our predictions given by `glm_predict`.

```{r accuracy-score}
accuracy_score(cancer_subset[["malignant"]], preds[[".prediction"]])
```

```{r precision-score}
precision_score(cancer_subset[["malignant"]], preds[[".prediction"]])
```

```{r recall-score}
recall_score(cancer_subset[["malignant"]], preds[[".prediction"]])
```

